Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-06 background.tex
remove TODOs in Section 2

\textbf{Progressive Adaptive:} In this policy, the decision to route minimally at each hop in the source group will be re-evaluated \TODO{packet granularity? flit granularity?}. Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang} \TODO{I thought PA does do re-evaluation?}. Progressive adaptive routing is capable of handling the case when a global channel is congested but the source router has not been informed yet~\cite{jiang}. The packet will take the non-minimal route only when the congestion is encountered.

>>>>

\textbf{Progressive Adaptive:} In this policy, the decision to route a packet minimally at each hop in the source group will be re-evaluated.
% \TODO{packet granularity? flit granularity? It is papacket granularity}. 
Any decision to route non-minimally at source router or at a subsequent hop is permanent and will not be re-evaluated~\cite{jiang}. 
%\TODO{I thought PA does do re-evaluation? PA do re-evaluate in source group only}. 
Progressive adaptive routing is capable of handling the case when a global channel is congested but the source router has not been informed yet~\cite{jiang}. The packet will take the non-minimal route only when the congestion is encountered.
